Laws for Creating Trust in the Blockchain Age

### 2017-07-27 tex/article.tex
Expand on how to realize land registration application
Please see included comments ("RV: ...") in .tex for TODOs.

The blockchain technology of today is sufficiently mature to start prototyping and understanding the (possible) advantages for land registration. 
This technology is not yet sufficiently understood to underpin such an essential public service, but it will be soon.
Similar to self-driving cars, it is likely that legal issues will decelerate technological progress.

>>>>

The blockchain technology of today is sufficiently mature to start prototyping and understanding the (possible) advantages for land registration. 
% RV: Expand a bit on how blockchains could be used for land registration:
Deeds that currently are stored in a centralized cadastral register,
  such as land purchases, mortgages and splits,
could easily be mapped onto transactions in a blockchain.
Things like inheritance rights or easements could be implemented through smart contracts % RV: Any nice reference that could be cited here?
which could rely on, e.g., the existence of attribute attestation transactions~(Section~\label{sec:trustchain}).
% RV: About query support:
In addition to recording the aforementioned transactions,
  land registration also requires its registers to be queryable and thus to be robust and highly available
  in order to provide services and certainty to citizens.
% RV: Please proofread the next few sentences and cite relevant references
Support for queries,
  such as ``what are the exact boundaries of my plot?''
  or ``what are the plots in this particular area?'',
  can be realized through a distributed search index on top of the blockchain.
An example of a real-world highly available distributed search index can be found in Tribler~(INCLUDE MOST RECENT RELEVANT TRIBLER PAPER HERE). % RV: Please add a citation here
%
While this technology is not yet sufficiently understood to fully underpin such an essential public service, it will be soon.
Similar to self-driving cars, it is likely that legal issues will decelerate technological progress.
